The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-31 cordillera-climate.tex
Clarify that phi is based on modern topography

A~pseudo-plastic sliding law \citep{aschwanden-etal-2013} relates the bed-parallel shear stress and the sliding velocity. The yield stress is modelled using the Mohr--Coulomb criterion. The till friction angle $\phi$ varies from 10 to 30\degree\ and is a~function of current bed elevation, with lowest values occurring at low elevations,

@@

where $\phi$ is given in degrees and $z$ in meters above current sea level. This model thus accounts for a~weakening of till associated with the presence of marine sediments \citep{martin-etal-2011,aschwanden-etal-2013}. Basal topography (Fig.~\ref{fig:topo}) is derived from the ETOPO1 combined topography and bathymetry dataset with a~resolution of 1\,arc-min \citep{data:etopo1}. Sea level is lowered by 120\,m and basal topography responds to ice load following a~regional isostasy model that includes lithospheric flexure and mantle relaxation \citep{lingle-clark-1985}.

>>>>

A~pseudo-plastic sliding law \citep{aschwanden-etal-2013} relates the bed-parallel shear stress and the sliding velocity. The yield stress is modelled using the Mohr--Coulomb criterion. The till friction angle $\phi$ varies from 10 to 30{\degree}. It is computed once at the beginning of the run, as a~function of modern bed elevation, with lowest values occurring at low elevations,

@@

where $\phi$ is given in degrees and $z$ in meters above current sea level. This model thus accounts for a~weakening of till associated with the presence of marine sediments \citep{martin-etal-2011,aschwanden-etal-2013}. Basal topography (Fig.~\ref{fig:topo}) is derived from the ETOPO1 combined topography and bathymetry dataset with a~resolution of 1\,arc-min \citep{data:etopo1}. Sea level is lowered by 120\,m and basal topography responds to ice load following a~regional isostasy model that includes lithospheric flexure and mantle relaxation \citep{lingle-clark-1985}. Till friction angle $\phi$ is not affected by bed elevation changes.
